My Cool Title

### 2019-05-05 paper.tex
Added paper layout to intro and section labels

\todo{Add paper layout}

\section{Previous Work}

\section{Active Vision System}

@@

\section{Human Controller}

@@

\section{Experiment Design}

@@

\section{Results}

%\subsection{Target Acquisition}

@@

\section{Conclusion}

>>>>

Section~\ref{sec:previous-work} discusses relevant work that has already been done, followed by a description of the active vision system and human controller in Sections~\ref{sec:active-vision} and~\ref{sec:human-controller} respectively. 
The experiments that were conducted in this work, and their results, are discussed in Sections~\ref{sec:experiments} and~\ref{sec:results}, followed finally by a short conclusion and discussion of the next steps for the project in Section~\ref{sec:conclusion}.

\section{Previous Work}\label{sec:previous-work}

\section{Active Vision System}\label{sec:active-vision}

@@

\section{Human Controller}\label{sec:human-controller}

@@

\section{Experiment Design}\label{sec:experiments}

@@

\section{Results}\label{sec:results}

@@

\section{Conclusion}\label{sec:conclusion}
